---
title: "Turorial"
output: 
  learnr::tutorial:
    progressive: true
    allow_skip: true
    df_print: default
runtime: shiny_prerendered
---


```{r setup, include=FALSE}
library(learnr)

tutorial_options(
  exercise.timelimit = 60,
  exercise.eval = TRUE
)

knitr::opts_chunk$set(
  echo = FALSE,
  # Can't be set in tutorial_options()
  exercise = TRUE,
  # Problematic arguments: If not set this way, output breaks code
  results = "hold",
  collapse = FALSE,
  error = FALSE,
  warning = FALSE,
  message = FALSE
)

```


## First steps with r2dii-data








These datasets support the implementation in R of
the software PACTA (Paris Agreement Capital Transition Assessment),
which is a free tool that calculates the alignment between financial
assets and climate scenarios (<https://2degrees-investing.org/>).
Financial institutions use PACTA to study how their capital
allocation impacts the climate. Because both financial institutions
and market data providers keep their data private, this package
provides fake, public data to enable the development and use of
PACTA in R.

## Installation

Before you install r2dii.analysis you may want to:

* [Try an rstudio.cloud project with this package already installed](https://rstudio.cloud/project/1424833).
* [Learn how to minimize installation errors](https://gist.github.com/maurolepore/a0187be9d40aee95a43f20a85f4caed6#installation).

When you are ready, install the released version of r2dii.data from CRAN with:

```r
install.packages("r2dii.data")
```

Or install the development version of r2dii.data with something like this:

```r
# install.packages("devtools")
devtools::install_github("2DegreesInvesting/r2dii.data")
```

[How to raise an issue?](https://2degreesinvesting.github.io/posts/2020-06-26-instructions-to-raise-an-issue/)

## Example

```{r example, exercise.setup='setup'}
library(r2dii.data)

head(data_dictionary)
```



