---
title: "Turorial"
output: 
  learnr::tutorial:
    progressive: true
    allow_skip: true
    df_print: default
runtime: shiny_prerendered
---


```{r setup, include=FALSE}
library(learnr)

tutorial_options(
  exercise.timelimit = 60,
  exercise.eval = TRUE
)

knitr::opts_chunk$set(
  echo = FALSE,
  # Can't be set in tutorial_options()
  exercise = TRUE,
  # Problematic arguments: If not set this way, output breaks code
  results = "hold",
  collapse = FALSE,
  error = FALSE,
  warning = FALSE,
  message = FALSE
)

```


## First steps with r2dii-match









These tools implement in R a fundamental part of
the software PACTA (Paris Agreement Capital Transition Assessment),
which is a free tool that calculates the alignment between financial
portfolios and climate scenarios (<https://2degrees-investing.org/>).
Financial institutions use PACTA to study how their capital
allocation impacts the climate. This package matches data from
financial portfolios to asset level data from market-intelligence
databases (e.g. power plant capacities, emission factors, etc.). This
is the first step to assess if a financial portfolio aligns with
climate goals.

## Installation

Before you install r2dii.match you may want to:

* [Try an rstudio.cloud project with this package already installed](https://rstudio.cloud/project/1424833).
* [Learn how to minimize installation errors](https://gist.github.com/maurolepore/a0187be9d40aee95a43f20a85f4caed6#installation).

When you are ready, install the released version of r2dii.match from CRAN with:

```r
# install.packages("r2dii.match")
```

Or install the development version of r2dii.match from GitHub with:

```r
# install.packages("devtools")
devtools::install_github("2DegreesInvesting/r2dii.match")
```

[How to raise an issue?](https://2degreesinvesting.github.io/posts/2020-06-26-instructions-to-raise-an-issue/)

## Example

```{r unlabeled-61, exercise.setup='setup'}
library(r2dii.data)
library(r2dii.match)
```

Matching is achieved in two main steps:

### 1. Run fuzzy matching

`match_name()` will extract all unique counterparty names from the columns: `direct_loantaker`, `ultimate_parent` or `intermediate_parent*` and run fuzzy matching against all company names in the `ald`:

```{r unlabeled-72, exercise.setup='unlabeled-61'}
match_result <- match_name(loanbook_demo, ald_demo)
match_result
```

### 2. Prioritize validated matches

The user should then manually validate the output of [match_name()], ensuring that the value of the column `score` is equal to `1` for perfect matches only.

Once validated, the `prioritize()` function, will choose only the valid matches, prioritizing (by default) `direct_loantaker` matches over `ultimate_parent` matches:

```{r unlabeled-83, exercise.setup='unlabeled-72'}
prioritize(match_result)
```

The result is a dataset with identical columns to the input loanbook, and added columns bridging all matched loans to their ald counterpart.

[Get started](https://2degreesinvesting.github.io/r2dii.match/articles/r2dii-match.html).
